Comparative safety and effectiveness of Pfizer BA.4-5 versus Sanofi during the spring 2023 COVID-19 booster vaccination programme in England: a matched cohort study in OpenSAFELY-TPP

### 2024-02-13 write-up/manuscript/manuscript.qmd
typos; per 10000 not 1000

During the spring 2023 COVID-19 booster programme in England, COVID-19-related hospital admissions were slightly more frequent following receipt of the Sanofi vaccine than the Pfizer BA.4-5 vaccine after matching on a number of important potential confounders. These finding were broadly consistent across subgroups, though estimated with less precision.

@@

The service adheres to the obligations of the UK General Data Protection Regulation (UK GDPR) and the Data Protection Act 2018. The service previously operated under notices initially issued in February 2020 by the the Secretary of State under Regulation 3(4) of the Health Service (Control of Patient Information) Regulations 2002 (COPI Regulations), which required organisations to process confidential patient information for COVID-19 purposes; this set aside the requirement for patient consent @WithdrawnWithdrawnCoronavirus2022. As of 1 July 2023, the Secretary of State has requested that NHS England continue to operate the Service under the COVID-19 Directions 2020 @COVID19PublicHealth. In some cases of data sharing, the common law duty of confidence is met using, for example, patient consent or support from the Health Research Authority Confidentiality Advisory Group @ConfidentialityAdvisoryGroup.

@@

This study was approved by the Health Research Authority (REC reference 20/LO/0651) and by London School of Hygeine and Tropical Medicine Ethics Board (reference 21863).

>>>>

During the spring 2023 COVID-19 booster programme in England, COVID-19-related hospital admissions were slightly more frequent following receipt of the Sanofi vaccine than the Pfizer BA.4-5 vaccine after matching on a number of important potential confounders. These findings were broadly consistent across subgroups, though estimated with less precision.

@@

The service adheres to the obligations of the UK General Data Protection Regulation (UK GDPR) and the Data Protection Act 2018. The service previously operated under notices initially issued in February 2020 by the Secretary of State under Regulation 3(4) of the Health Service (Control of Patient Information) Regulations 2002 (COPI Regulations), which required organisations to process confidential patient information for COVID-19 purposes; this set aside the requirement for patient consent @WithdrawnWithdrawnCoronavirus2022. As of 1 July 2023, the Secretary of State has requested that NHS England continue to operate the Service under the COVID-19 Directions 2020 @COVID19PublicHealth. In some cases of data sharing, the common law duty of confidence is met using, for example, patient consent or support from the Health Research Authority Confidentiality Advisory Group @ConfidentialityAdvisoryGroup.

@@

This study was approved by the Health Research Authority (REC reference 20/LO/0651) and by London School of Hygiene and Tropical Medicine Ethics Board (reference 21863).
